Assessing the Impact of Financial Assistances on Business and Income Outcomes: A Gender-Specific Analysis

### 2024-02-14 paper/paper.qmd
paper.qmd

We replicate the paper by Bruno Crépon, Mohamed El Komi, and Adam Osman, focusing on the following research questions: 
* Which type of financial support has the greatest impact on business ownership of microenterprises? 
* Which type of financial support has the greatest impact on monthly profit of microenterprises? 
* Which type of financial support has the greatest impact on monthly revenue of microenterprises? 
* Which type of financial support has the greatest impact on new asset of microenterprises? 
* How do gender of entrepreneurs mediate the effects of financial support on microenterprise performance?

They are important for the decision-making of governments and institutions, helps them utilize their budget and generate the best outcome. Our estimands quantify the expected impact of the type of financial support on our main variables:
- **Type of Financial Support**: Examining the differential impact of microcredit, in-kind grants, and cash grants on microenterprise outcomes.
- **Business Ownership**: Estimating the effect of financial support on the probability of owning a business post-intervention.
- **Monthly Expenses**: Assessing how different types of financial support influence the monthly expenses of businesses.
- **Monthly Profits**: Determining the role of financial support in enhancing business profitability.
- **Monthly Revenue**: Evaluating the impact of financial support on business sales activity.
- **New Assets**: Measuring the ability of financial support to enable businesses to acquire new assets post-intervention.

@@

We assessed the impact of financial interventions using several outcome variables:
- **Business Ownership (`hasbiz`)**: A binary outcome variable indicating whether an entrepreneur owned a business post-intervention, serving as a direct measure of the success of the financial support. 
- **New Business Assets (`new_biz_assets`)**: A continuous variable representing the total value of new assets acquired by the business post-intervention. This variable captures the ability of a business to expand and invest, which is central to long-term growth.
- **Monthly Expenses**: A continuous variable summing all monthly costs incurred by the business. This reflects the immediate financial activity and potential expansion resulting from the intervention. 
- **Monthly Profits (`monthly_profits`)**: Calculated as the difference between revenue and expenses, this variable measures the profitability of the business, a key indicator of financial viability.
- **Monthly Revenue (`monthly_revenue`)**: The total monthly sales before costs, representing the operational turnover and market activity of the business.

@@

We also computed income-related variables that aggregate various income sources:
- **Labour Income (`labour_inc`)**: Summing monthly profits, wages, and other labour income, providing a comprehensive view of the entrepreneur's earnings.
- **Total Income (`total_inc`)**: A broader measure of income that includes profits, rent, other incomes, government support, and transfers, offering a complete picture of the financial benefits of the intervention.

>>>>

We replicate the paper by Bruno Crépon, Mohamed El Komi, and Adam Osman, focusing on the research question: Does the type of financial support have an impact on the overall performance of enterprises, and is this impact related to the gender of the entrepreneur? The three treatments are microcredit, in-kind grants, and cash grants. Our estimands quantify the expected impact of the type of financial support on our main variables:
- **Business Ownership**: Estimating the effect of financial support on the probability of owning a business post-intervention.
- **Monthly Expenses**: Assessing how different types of financial support influence the monthly expenses of businesses.
- **Monthly Profits**: Determining the role of financial support in enhancing business profitability.
- **Monthly Revenue**: Evaluating the impact of financial support on business sales activity.
- **New Assets**: Measuring the ability of financial support to enable businesses to acquire new assets post-intervention.
- **Labour Income**: Summing monthly profits, wages, and other labour income, providing a comprehensive view of the entrepreneur's earnings.
- **Total Income**: A broader measure of income that includes profits, rent, other incomes, government support, and transfers, offering a complete picture of the financial benefits of the intervention.

@@

We assessed the impact of financial interventions using several outcome variables:
- **Business Ownership (`hasbiz`)**: A binary outcome variable indicating whether an entrepreneur owned a business. An individual does not have business if they do not have project or have no income source.
- **New Business Assets (`new_biz_assets`)**: A continuous variable representing the total value of new assets acquired by the business post-intervention. It is defined by the sum of inventory stocks, finished goods, liquid cash reserves, value of new business premises, recently purchased land, furniture, machinery and equipment, vehicles, and the cost of maintenance for these assets. 
- **Monthly Expenses**: A continuous variable summing all monthly costs incurred by the business. This reflects the immediate financial activity and potential expansion resulting from the intervention.
- **Monthly Profits (`monthly_profits`)**: Calculated as the difference between revenue and expenses, this variable measures the profitability of the business, a key indicator of financial viability.
- **Monthly Revenue (`monthly_revenue`)**: The total monthly sales before costs, representing the operational turnover and market activity of the business.

@@

We also computed income-related variables that aggregate various income sources:
- **Labour Income (`labour_inc`)**: It is calculated by summing the monthly profit, wage income, and other labour income source.
- **Total Income (`total_inc`)**: It is calculated by summing the monthly profit, wages, rental income from assets, other income streams not categorized as labor income, government support values, and received transfers.
